An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-08-05 poly-embed-journal/poly-embed-journal.tex
Pre meeting small edits

Note however that the number of dimensions $d$ required could be as large as $n = |\Y|$, which is particularly undesirable in structured prediction and information retrieval problems where the number of outcomes is exponential.
Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the prediction dimension $d$ for consistent convex surrogates and embeddings.
%\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}

\proposedadd{Moreover, to construct an embedding of dimension $n-1$ instead of $n$ (see~\citet{finocchiaro2020embedding} for significance of dimension),  consider some invertible linear transformation $A : \reals^n \to \reals^{n-1}$ that maps to an affine subspace.
Take $L' : \reals^{n-1} \to \reals^\Y$ as $x \mapsto L(A^{-1}(x))$ and $L$ defined as above, so that $\inprod{\ell(r)}{p} = \inprod{L(\varphi(r))}{p} = \inprod{L'(A^{-1}(\varphi(r)))}{p} $ for all $p \in \simplex$.
The Bayes risks $\risk{L}(p)$ and $\risk{L'}(p)$ are equal for all $p \in \simplex$; thus, the result holds in $n-1$ dimensions as well.}\jessiet{Leaving this change in the macro for proofreading.}

>>>>

Note however that the number of dimensions $d$ required could be as large as $n = |\Y|$, which is particularly undesirable in structured prediction and information retrieval problems where the number of outcomes is exponential.
Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the prediction dimension $d$ for consistent convex surrogates and embeddings.
Moreover, to construct an embedding of dimension $n-1$ instead of $n$, consider an invertible linear transformation from $\reals^n \to \reals^{n-1}$ and re-define the loss appropriately so Bayes Risks match.
%\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}

%Moreover, to construct an embedding of dimension $n-1$ instead of $n$ (see~\citet{finocchiaro2020embedding} for significance of dimension),  consider some invertible linear transformation $A : \reals^n \to \reals^{n-1}$ that maps to an affine subspace.
%Take $L' : \reals^{n-1} \to \reals^\Y$ as $x \mapsto L(A^{-1}(x))$ and $L$ defined as above, so that $\inprod{\ell(r)}{p} = \inprod{L(\varphi(r))}{p} = \inprod{L'(A^{-1}(\varphi(r)))}{p} $ for all $p \in \simplex$.
%The Bayes risks $\risk{L}(p)$ and $\risk{L'}(p)$ are equal for all $p \in \simplex$; thus, the result holds in $n-1$ dimensions as well.
%\jessiet{Leaving this change in the macro for proofreading.}
